Transient Corotating Clumps Around Adolescent Low-Mass Stars From Four Years of TESS

### 2023-11-01 paper/ms.tex
propagate updated SED prior change into ms
per reviewer's suggestion

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess.  We omitted WISE bands $W3$ and $W4$ due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  Given our selection criteria for the stars,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{N}(3000, 1000), \\
  R_\star / R_\odot  &\sim \mathcal{T}_{\rm N}(0.5, 0.3, 0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
truncated normal distribution with mean $\mu$, standard deviation
$\sigma$, and lower and upper bounds $a$ and $b$.  We validated our
chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
Finally, using \texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we
sampled the posterior probability assuming the default Gaussian
likelihood, and set a stopping threshold of ${\rm d}\log \mathcal{Z} <
0.01$, where $\mathcal{Z}$ denotes the evidence.

@@

To date, the only stars reported to show the CPV phenomenon are M
dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
massive CPVs in our sample, TIC~405754448 and TIC~405910546, were
assigned masses of $\approx$0.82\,$M_\odot$ and
$\approx$0.60\,$M_\odot$ respectively.  The next-highest mass in our
sample belongs to TIC~59836633 ($\approx$0.48\,$M_\odot$), with all
remaining CPVs having masses $\lesssim$0.40\,$M_\odot$.

>>>>

For the SED fitting, we used \texttt{astroARIADNE}
\citep{2022MNRAS.513.2719V}.  We adopted the BT-Settl stellar
atmosphere models \citep{Allard2012} assuming the
\citet{2009ARA&A..47..481A} solar abundances, and the
\citet{2006MNRAS.368.1087B} water line lists.  The broadband
magnitudes we considered included $GG_{\rm BP}G_{\rm RP}$ from Gaia
DR2, $Vgri$ from APASS, $JHK_{\rm S}$ from 2MASS, SDSS $riz$, and the
WISE $W1$ and $W2$ passbands.  We omitted UV flux measurements from
our SED fit to avoid any possible bias induced by chromospheric UV
excess.  We omitted WISE bands $W3$ and $W4$ due to reliability
concerns.  \texttt{astroARIADNE} compares the measured broadband flux
measurements against pre-computed model grids, and by default fits for
six parameters: $\{ T_{\rm eff}, R_\star, A_{\rm V}, \log g, [{\rm
Fe/H}], d \}$.  The distance  prior is drawn from
\citet{2021AJ....161..147B}.  The surface gravity and metallicity are
generally unconstrained.  Given our selection criteria for the stars,
we assumed the following priors for the temperature, stellar size, and
extinction:
\begin{align}
  T_{\rm eff} / {\rm K}    &\sim \mathcal{U}(2000, 8000), \\
  R_\star / R_\odot  &\sim \mathcal{U}(0.1, 1.5), \\
  A_{\rm V} / {\rm mag}    &\sim \mathcal{U}(0, 0.2),
\end{align}
for $\mathcal{N}$ the Gaussian and $\mathcal{U}$ the uniform
distributions, and $\mathcal{T}_{\rm N}(\mu, \sigma, a, b)$ a
truncated normal distribution with mean $\mu$, standard deviation
$\sigma$, and lower and upper bounds $a$ and $b$.  We validated our
chosen upper bound on $A_{\rm V}$ using a 2MASS color-color diagram.
Finally, using \texttt{Dynesty} \citep{2020MNRAS.493.3132S}, we
sampled the posterior probability assuming the default Gaussian
likelihood, and set a stopping threshold of ${\rm d}\log \mathcal{Z} <
0.01$, where $\mathcal{Z}$ denotes the evidence.

@@

To date, the only stars reported to show the CPV phenomenon are M
dwarfs, with typical stellar masses $\lesssim$0.3\,$M_\odot$
\citep{2017AJ....153..152S,2022AJ....163..144G}.  However the two most
massive CPVs in our sample, TIC~405754448 and TIC~405910546, were
assigned masses of $\approx$0.82\,$M_\odot$ and
$\approx$0.60\,$M_\odot$ respectively.  The next-highest mass in our
sample belongs to TIC~59836633 ($\approx$\replaced{0.48}{0.45}\,$M_\odot$), with all
remaining CPVs having masses $\lesssim$0.40\,$M_\odot$.
